---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

This is an EXPERIMENTAL standalone viewer, written in Go, for the super-cool 
{httpgd} package `remotes::install_github("nx10/httpgd")`.

The Windows viewer is not built yet because I haven't got round to it because
I detest Windows.

The goal is to have a "Quartz"-like window (for folks familiar with that on macOS) with full functionality. Right now, it's just a basic viewer (and 'save' doesn't work for some reason that I'm trying to figure out.)

If I were you, I wouldn't waste time on this package as it'll likely just get Sherlocked w/o notice by RStudio at some point and baked into their ecosystem. I made it mainly for myself as I also detest using the "browser for research" as an application runner.

I'm also just as likely to add an {httpgd} viewer functionality into RSwitch since it already functions as an RStudio Server client and it won't take much to have it work with {httpgd} directly (or via this package).

If you don't trust the pre-built viewers, `tools-raw` has what you need to make your own. They go into `tools::R_user_dir(package = "grandview"), "app")` and for the macOS one you'll need to use your own signing cert (you may need to right-click open my built one once due to faux security theatre by Apple).

Because I rely on `tools::R_user_dir()` this package requires R 4.0.0+. That was a deliberate choice since the adoption rate for R 4.0.0+ is likely low (so I have time to refine this package) and I'd rather rely on it than {rappdirs}.

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(grandview)

# current version
packageVersion("grandview")

```

```{r eval=FALSE}
install_viewer() # you'll get prompts to do this

hgd() # it accepts params which will get passed to the viewer

# plot stuff

dev.off()
```

## grandview Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
